\documentclass[11pt, a4paper]{article}
\usepackage{fullpage}
\usepackage[USenglish]{babel}

\title{Master Thesis -  Security Aspects in Virtual Networks\\ \textbf{SITREP 1}}
\author{\textbf{Laurent De Wilde} \\ Master of Science in the Applied Computer Science \\ Vrije Universiteit Brussel}


\begin{document}
\maketitle

\section{Work done}

On Friday November 14, I had an appointment with Prof. M. Timmerman to discuss some practical details about the first steps to start the thesis. This is an overview of the accomplished work:
\begin{itemize}
\item Saturday November 15: installation and resetting of the Netgear router, as well as some first configuration of the router. Of course, I downloaded the documentation/manual of the appropriate router. I set up a temporary tiny network at home to configure the router consisting of the router, a switch and my laptop.
\item Sunday November 16: continued the configuration of the router and read the PhD proposal of Joseph.
\end{itemize}

\section{Planning}

This week I expect to provide an answer to the question of how many IP addresses I will need. Most likely, the answer will be 1. Normally, the configuration of the router should be completed by the end of this week. Also, I will make an appointment with Fei Guan concerning the installation of the `pizza servers'.

\section{Problems}

No problems have been encountered so far.

\section{Issues}

For now, no issues have been encountered.

\section{Assistance}

I will probably need some assistance of Fei Guan to install the `pizza servers'.

\end{document}