\documentclass[11pt, a4paper]{article}
\usepackage{fullpage}
\usepackage[USenglish]{babel}

\title{Master Thesis -  Security Aspects in Virtual Networks\\ \textbf{SITREP 2}}
\author{\textbf{Laurent De Wilde} \\ Master of Science in the Applied Computer Science \\ Vrije Universiteit Brussel}


\begin{document}
\maketitle

\section{Work done}

This is an overview of the accomplished work:
\begin{itemize}
\item Tuesday November 18 and Wednesday November 19: upgraded the firmware of the NetGear router to the latest version available.
\item Friday November 21: Made an appointment with Ms Fei Guan to install Windows Server 2012 R2 on one of the `pizza servers'. We placed the server on the central desk of the Ems Lab and I first created a bootable USB drive to be able to install WS2012 since the server obviously doesn't have a DVD drive. When completed, I deleted every partition on the RAID and SSD and tried to install WS2012 on the SSD. However, that would not succeed. After doing some research, it turns out one cannot install an OS from a USB 3.0 drive. I've had the same problem with Windows 8 at home and, as it turns out, also on this server.\\
I will return on Monday morning to complete the installation. In the meantime, I created another bootable USB drive with WS2012. This time however, a USB 2.0 drive.
\item Monday November 24: Returned to the Ems Lab to continue the installation of Windows Server 2012 on the `pizza server' and the installation completed successfully.
\end{itemize}

\section{Planning}

As the configuration of the router is complete, it turns out I will use just one IP address.

\section{Problems}

Unable to install WS2012 using a USB 3.0 drive. I will retry the installation on Monday using a USB 2.0 drive.

\section{Issues}

See ``Problems''.

\section{Assistance}

For now, no assistance is needed.

\end{document}